Effect of character correlation

### 2017-09-12 Analysis/EffectCorrelationStats.Rmd
updated analysis

## Print the results
wx_RF_best
wx_Tr_best
wx_RF_null
wx_Tr_null
```

>>>>

## Print the results
round(wx_RF_best, digit = 3)
round(wx_Tr_best, digit = 3)
round(wx_RF_null, digit = 3)
round(wx_Tr_null, digit = 3)
```

```{r}
library(xtable)
## Combining both tables (for paper)
col_description <- matrix(ncol = 3,
    data = c(rep(rep(c("25", "75", "150"), each = 3), 2),
             rep(c("100", "350", "1000"), 6),
             rep(c("Bay.", "Par."), each = 9)), dimnames = NULL)

matrix_out <- cbind(as.data.frame(col_description), as.data.frame(cbind(bc_RF_best[,1], wx_RF_best[,1:2], bc_RF_best[,2], wx_RF_best[,3:4], bc_RF_best[,3], wx_RF_best[,5:6])))

rownames(matrix_out) <- NULL

xtable(matrix_out, caption = "CAPTION", label = "LABEL", round = 3)

(bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff))
(bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff))
(bc_RF_null <- apply.test(whole_data, "RF", "null", bhatt.coeff))
(bc_Tr_null <- apply.test(whole_data, "Triples", "null", bhatt.coeff))
